PANCHANGE_descriptives

### 2020-11-06 PANCHANGE_exclusion_descriptives.Rmd
added code to assess accuracy of retro change vs pre_pan change

@@

#Edit the gad sum retro score as follows: if there is a missing value in the retro sum score, give it the baseline sum score, else leave it as it is

>>>>

dat.raw <- dat.raw %>%
    mutate(gad.change.retro.accurate = if_else(dat.raw$gad.pandemic.change.group == "Better" &
                                             dat.raw$gad.diff_score_retro_prepan == 0 |
                                             dat.raw$gad.pandemic.change.group == "Worse" &
                                             dat.raw$gad.diff_score_retro_prepan == 0, 1, 3 ))
dat.raw <- dat.raw %>%
  mutate(gad.change.retro.accurate = if_else(dat.raw$gad.pandemic.change.group == "Better" &
                                             dat.raw$gad.diff_score_retro_prepan >= -3 &
                                             dat.raw$gad.diff_score_retro_prepan <= 3 &
                                             dat.raw$gad.change.retro.accurate_temp != 1 |
                                             dat.raw$gad.pandemic.change.group == "Worse" &
                                             dat.raw$gad.diff_score_retro_prepan >= -3 &
                                             dat.raw$gad.diff_score_retro_prepan <= 3 &
                                             dat.raw$gad.change.retro.accurate_temp != 1,  2, gad.change.retro.accurate))

@@

#Edit the gad sum retro score as follows: if there is a missing value in the retro sum s0core, give it the baseline sum score, else leave it as it is
